%% Start of file `template.tex'.
%% Template copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,letterpaper]{moderncv}

%\usepackage{hyperref}
\usepackage{color}
\usepackage{fontspec}

% THEMES
% Optional arguments are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casual}
\moderncvtheme[blue]{classic}
%\moderncvtheme[grey]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.7cm}                    % The width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}} % Only for the classic theme if you want to change the width of your name placeholder (to leave more space for your address details)
\AtBeginDocument{\recomputelengths}                     % Required when changes are made to page layout lengths

% CHARACTER ENCODING
\usepackage{xunicode}
\usepackage{xltxtra}
%\usepackage[utf8]{inputenc}            % Package inputenc is no not required when using xelatex
\defaultfontfeatures{Mapping=tex-text}  % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% FONTS
%\setromanfont[Ligatures={Common}, Numbers={OldStyle}]{Linux Libertine O}
%\setmonofont[Scale=0.8]{DejaVuSansMono}
%\setsansfont[Scale=0.9]{OptimaLTStd}

% ---- CUSTOM AMPERSAND
%\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}

% PERSONAL DATA
\firstname{Yuliang}
\familyname{Jin}
%\title{Yuliang's Résumé}                                                       % Optional, remove the line if not wanted
%\address{1406, \# 3 Fangushuijun, \#2 Tuofangying S. Rd.}{Chaoyang, Beijing}   % Optional, remove the line if not wanted
\mobile{\texttt{+86 18511663768}}                                               % Optional, remove the line if not wanted
%\phone{\texttt{+1 (347) 450-5748}}                                             % Optional, remove the line if not wanted
%\fax{fax}                                                                      % Optional, remove the line if not wanted
\email{yuljin@microsoft.com}                                                    % Optional, remove the line if not wanted
%\email{yuljin.ms@gmail.com}                                                    % Optional, remove the line if not wanted
%\homepage{gnailuy.com}                                                         % Optional, remove the line if not wanted
%\extrainfo{github.com/gnailuy}                                                 % Optional, remove the line if not wanted
%\photo[64pt]{dont_panic.png}                                                   % The picture must be resized to 64pt
%\quote{Circuit bender, kernel hacker, robot builder, urban explorer, trombone playerer.}

% To show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% Bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

%----------------------------------------------------------------------------------
% CONTENT
%----------------------------------------------------------------------------------
\begin{document}

\maketitle

\section{Professional Summary}
    \cvline{}{
        \begin{itemize}
            \item Experienced Senior Software Engineer with the Messaging and Realtime Analytics team at Microsoft Azure.
            \item Actively engaged in the design and implementation of new features for the Microsoft Fabric Eventstream service.
            \item Enhanced the monitoring and debugging tooling for Azure Stream Analytics service on multiple platforms.
            \item Coordinated the DRI (on-call) team schedules and incident tracking, facilitating effective cross-team communication.
            \item Previously a Data and Backend Expert for a startup team, responsible for developing a wind turbine monitoring system from scratch.
            \item Key contributor to Alibaba's Mobile App Analytics platform as a Senior Data Platform Engineer, driving its rapid growth and development.
            \item Demonstrated proficiency in a broad range of areas, including but not limited to Full-Stack Development, Big Data Analytics, Cloud Computing, and Distributed Systems.
            \item Long time GTD practitioner and self-learner with stable productivity and reliability.
        \end{itemize}
    }{}{}{}{}

\section{Work Experience}
    \cventry{2019.01-Present}{Microsoft Azure}{Senior Software Engineer}{Beijing}{}{}
    \cventry{2017.08-2018.06}{Startup Team}{Data and Backend Expert}{Beijing}{}{}
    \cventry{2013.04-2017.07}{Alibaba Umeng}{Senior Data Platform Engineer}{Beijing}{}{}

\cvline{}{}

\section{Projects}
    \cventry{2019.01-Present}{Messaging and Realtime Analytics}{}{}{}{}
    \subsection{\small\emph{Microsoft, Senior Software Engineer}}
    \cvlistitem{Designed and delivered both frontend and backend features for the Microsoft Fabric Eventstream.}
    \cvlistitem{Developed new features and maintained the Visual Studio and Visual Studio Code extensions for the Azure Stream Analytics service.}
    \cvlistitem{Expanded the job monitoring web APP for Visual Studio Code to accommodate Azure Synapse Streaming and Azure Portal.}
    \cvlistitem{Developed an internal web tool to expose physical topologies for Azure Stream Analytics.}
    \cvlistitem{Coordinated the DRI (on-call) for Azure Stream Analytics service in the Beijing team.}
    \cvlistitem{Stack: Azure, C\#, Typescript, .Net, React, Visual Studio, Visual Studio Code.}

    \cventry{2017.08-2017.10}{Wind Turbine Performance Monitoring}{}{}{}{}
    \subsection{\small\emph{Startup Team, Main Developer}}
    \cvlistitem{Developed a monitoring system for wind turbines from scratch, handling both backend and data development.}
    \cvlistitem{Designed and implemented modularized framework supporting data collection, cleansing, calculation, and report generation.}
    \cvlistitem{Developed calculation modules which processed the collected data and generated unified JSON reports and images.}
    \cvlistitem{Created a report generation service that utilized the JSON data and images to render final reports for different clients.}
    \cvlistitem{Stack: Python, NumPy, SciPy, Matplotlib, Pandoc, MongoDB, Spark Streaming, Redis.}

    \cventry{2013.04-2017.07}{Data Platform ETL}{}{}{}{}
    \subsection{\small\emph{Alibaba, Senior Data Platform Engineer}}
    \cvlistitem{Contributed to the development of the largest mobile APP analytics platform in China, focusing primarily on the data platform ETL system.}
    \cvlistitem{Designed and sustained MapReduce/Spark jobs for statistical analyses on large dataset.}
    \cvlistitem{Undertook a significant refactoring of most ETL jobs to improve stability and accuracy.}
    \cvlistitem{Assisted in upgrading and scaling the cluster from 10 nodes to over 1,000 nodes to accommodate business growth.}
    \cvlistitem{Developed the ETL job scheduler for batch pipelines.}
    \cvlistitem{Participated in the development of a unified ID service and other API services.}
    \cvlistitem{Stack: Java, Scala, Python, Hadoop, MapReduce, Spark, Kafka, HBase, Hive, Netty.}

\cvline{}{}

\section{Education}
    \cventry{2010.09-2013.03}{Master of Computer Engineering}{Harbin Engineering University}{}{}{
        \begin{itemize}
            \item \textit{Honors:} Awarded the National Scholarship for academic excellence
        \end{itemize}
    }
    \cventry{2006.09-2010.07}{Bachelor of Computer Science and Technology}{Harbin Engineering University}{}{}{}

\cvline{}{}

\section{Technical Skills}
    \cvline{}{
        \begin{itemize}
            \item Proficient in computer science fundamentals, including strong algorithmic, design, and programming skills.
            \item Extensive experience in full-stack development, encompassing frontend, backend, data, desktop applications, and system programming on Linux.
            \item Deep understanding of the Azure cloud ecosystem and other major cloud services.
            \item Expertise in Big Data technologies, including Azure Stream Analytics, Hadoop, Spark, HBase, and Kafka.
            \item Proficiency in multiple programming languages such as C/C++, C\#, Typescript, Python, Java, Scala, and Golang.
            \item Experienced in incident management and troubleshooting in live production environments.
        \end{itemize}
    }

\cvline{}{}

% \nocite{DBLP:conf/issre/ZhaoJTM11,DBLP:journals/jetc/ZhaoJTMW14}
% \bibliographystyle{plain}
% \bibliography{publications}

% \cvline{}{}

\section{Languages}
    \cvlanguage{English}{Professional Working Proficiency}{}
    \cvlanguage{Mandarin}{Native}{}
    % \cvlanguage{Italian}{Elementary Proficiency}{Self-taught}

\end{document}

%\section{Experience}
%\subsection{Vocational}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline%
%Detailed achievements:%
%\begin{itemize}%
%\item Achievement 1;
%\item Achievement 2, with sub-achievements:
%  \begin{itemize}%
%  \item Sub-achievement (a);
%  \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
%    \begin{itemize}
%    \item Sub-sub-achievement i;
%    \item Sub-sub-achievement ii;
%    \item Sub-sub-achievement iii;
%    \end{itemize}
%  \item Sub-achievement (c);
%  \end{itemize}
%\item Achievement 3.
%\end{itemize}}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newlineDescription line 2}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description}

%\section{Computer skills}
%\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvcomputer{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvcomputer{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

%\section{Interests}
%\cvline{hobby 1}{\small Description}
%\cvline{hobby 2}{\small Description}
%\cvline{hobby 3}{\small Description}

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5 \cite{book1}}
%\cvlistdoubleitem{Item 3}{}

% Publications from a BibTeX file without multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% for BibTeX numerical labels
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}   % 'publications' is the name of a BibTeX file

%% end of file `template.tex'.
